[Fall 2023: This is an optional DIY just for fun]

This is a challenging and a \lq\lq thinking" problem.

Planet Troisdoigts has just heard your presentation on using
two's complement representation to represent 32-bit signed integers.
They are impressed and want the same thing for their computer
systems.
But ... they prefer base 3.
Since you are an expert on two's complement, they have commissioned
your company to design a base-3 computer system that uses what they
are calling the
\lq\lq three's complement" representation for representing
signed integers.
The commission fee was high and delicious.
So your boss has accepted the project and insists that you design the system.

Suppose you are using 3 base-3 symbols. (So there are 27 patterns.)

\begin{enumerate}
\item[(a)] How would you represent positive and negative numbers?
What negative numbers are represented?
What positive numbers are represented?
Draw a table that translate between Earthling signed base-10 numbers
and three's complement base-3 numbers.

\item[(b)] How would you compute
$5 + 2$ (in Earthling notation) in 3 base-3 symbols?

\item[(c)] How would you compute, in Earthling notation,
the expression $5 - 2$ in 3 base-3 symbols?
Of course from your experience with 32-bit two's complement,
you would want to compute this using 3 base-3 symbols of addition
and also you want to convert 2 to it's \lq\lq three's complement"
of 3 base-3 symbols, and then perform addition on \lq\lq $5 + (-2)$",
so to speak.
How would you do it?!?

\item[(d)]
What about multiplication?

\end{enumerate}
